\section{Timeline}

    \subsection*{Before May 9}
    Meet the mentors, discuss with them the proposed timeline,
    deliverables and share ideas.

    \subsection*{May 9 -- May 23}
    Search in the literature for algorithms that solve the min-cost flow problem
    with convex cost functions. 
    Follow the bitcoin and lightning seminars.
    
    \subsection*{May 23 -- June 6}
    Design of a standalone C++ library for solving the min-cost flow problem.
    Implementation of a textbook efficient solution to the linear min-cost flow
    problem, the \emph{Excess Scaling} algorithm described in 
    \cite{ahuja1993network} section 7.9.
    This linear MCF solver can be used to solve convex cost problems with a
    tuneable linear approximation by decomposing the non-linear cost arcs into
    several linear cost arcs.
    Set up a simple set of unit tests for correctedness and CI for the library
    repository.
    
    \subsection*{June 6 -- June 20}
    Use the code to reproduce the results 
    of Pickhardt's \emph{Payment Simulation} Jupyter Notebook.
    Implementation of a textbook solution: the capacity scaling algorithm described in
    \cite{ahuja1993network} section 14.5. This algorithm is a generalization of
    the \emph{Excess Scaling}, hence it shouldn't be too difficult to adapt
    the linear MCF already implemented to the general convex cost case.
    
    \subsection*{June 20 -- July 4}
    Benchmark the canditate solutions.
    Optimize the code to find a good tradeoff of runtimes and probability of
    success.
    Parallelization of the time critical routines.
    
    \subsection*{July 4 -- July 18}
    Implementation of a small C-lightning plugin to demonstrate the use of the
    library.
    
    \subsection*{July 18 -- August 1}
    Document the library and buffer time for unfinished issues.
    
    \subsection*{August 1 -- August 15}
    Preparation of the final report and draft the research article.
    
    \subsection*{August 15 -- August 22}
    Submission of the final project report.
